\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2011-02-06 article.tex
Moved tables 1 and 2 around

% what are the groups of techniques?

  Table 2: Percent distribution by arm per category

  In terms of category distribution, there are more blocks with the left side
  than there are with the

  It is worth noting that there are more blocks with the left side than with
  the right side. That is, there are more attacks with the right arm than with
  the left arm.

@@

>>>>

@@

  In terms of category distribution, there are more blocks with the left side
  than there are with the right side. A side effect is that there are more
  attacks with the right side, than with the left side (Table
  \ref{tab:table2}).
